Leadership across cultures and contexts: an exploratory analysis

### 2020-05-19 leadership_across_cultures_contexts.Rmd
RE-Submitted version.

---
title: "Leadership across cultures and contexts: an exploratory analysis"
author: "Zachary H. Garfield, Kristen L. Syme, and Edward H. Hagen"
date: "4/25/2019"
output: 
  bookdown::html_document2:
    number_sections: false
bibliography: Leader2.bib
csl: apa-6th-edition.csl
---

@@

```{r grouptype, fig.width=20, fig.height=10, fig.cap="The distribution of text records by subsistence and group context. Areas of the bars are proportional to the number of text records in that category."}
ggsave(file="Figures/group_subsis.pdf", plot_group_subsis, width=16, height=6)
plot_group_subsis
```

@@

The *Competencies* feature combined dimensions of prestige-style leadership, such as knowledge and experience, with dimensions of dominance-style leadership, such as aggressiveness and feared. It also included supernatural qualities. Shamans and other leaders with supernatural qualities were surprisingly common in the ethnographic record. Of our `r nrow(leader_text2)` text records, `r sum(df_shaman$shaman)` used the word "shaman", `r supernatural_n` provided evidence for supernatural leader qualities, and `r sum(df_shaman$shamanism)` provided evidence for one or both (`r shamanism_pct`% of all text records). We term the latter variable *Shamanism*. We fit a logistic elasticnet model of *Shamanism* as a function of all leadership dimensions (minus *Supernatural*). This model revealed that shaman leaders combined dimensions of dominant leaders (*Feared*) with dimensions of prestigious leaders (*Medical functions*, which are a form of knowledge or expertise, and *Experienced/accomplished*). See Figure \@ref(fig:shamanism).

@@

```{r shamanregion, fig.cap="Estimated marginal means of evidence for shamanism by region, controlling for subsistence strategy. From a logistic mixed effects model with random intercepts for author nested within culture. Values are on the response scale (probability)."}
ggemmeans(shaman_emmeans_region) + labs(x = '\nProbability', y = '')
```

>>>>

---
title: "Leadership across cultures and contexts: an exploratory analysis"
author: "Zachary H. Garfield, Kristen L. Syme, and Edward H. Hagen"
date: "4/25/2019"
output: 
  bookdown::html_document2:
    number_sections: true
bibliography: Leader2.bib
csl: apa-6th-edition.csl
---

@@

```{r grouptype, fig.width=20, fig.height=10, fig.cap="The distribution of text records by subsistence and group context. Areas of the bars are proportional to the number of text records in that category."}
ggsave(file="Figures/group_subsis.pdf", plot_group_subsis, width=18, height=7)
plot_group_subsis
```

@@

The *Competencies* feature combined dimensions of prestige-style leadership, such as knowledge and experience, with dimensions of dominance-style leadership, such as aggressiveness and feared. It also included supernatural qualities. Shamans and other leaders with supernatural qualities were surprisingly common in the ethnographic record. Of our `r nrow(leader_text2)` text records, `r sum(df_shaman$shaman)` used the word "shaman", `r supernatural_n` provided evidence for supernatural leader qualities, and `r sum(df_shaman$shamanism)` provided evidence for one or both (`r shamanism_pct`% of all text records). We term the latter variable *Shamanism*. We fit a logistic elasticnet model of *Shamanism* as a function of all leadership dimensions (minus *Supernatural*). This model revealed that shaman leaders combined dimensions of dominant leaders (*Feared*) with dimensions of prestigious leaders (*Medical functions*, which are a form of knowledge or expertise, and *Experienced/accomplished*). See Figure S\@ref(fig:shamanism).

@@

```{r shamanregion, fig.cap="Estimated marginal means of evidence for shamanism by region, controlling for subsistence strategy. From a logistic mixed effects model with random intercepts for author nested within culture. Values are on the response scale (probability)."}
ggsave(filename = 'Figures/shaman_emmeans_region.pdf', ggemmeans(shaman_emmeans_region) + labs(x = '\nProbability', y = ''))
ggemmeans(shaman_emmeans_region) + labs(x = '\nProbability', y = '')
```
